---
title: "Default and Endorsement"
author: "Jin Miao"
date: ''
output:
  html_document: default
  
---
#Summary 
*(each item is following their corresponding result table)*:

1. Compared with non-default, the proportion of choosing 1 in the Default group is significantly higher.

2. Both social endorsement and company endorsement have signficant positive effects on the probability of choosing 1. 

3. EndorsementCondition does not have any significant effects on both choice and defaultchoice. 

4. Baltho has significant effect on choice while the effect of smrd on choice is insignificant.

5. baltho and smrd do not depend on default setting.

6. Reverse to Summary 4, Baltho has insignificant effect on choice while the effect of smrd on choice is significant.

7. Covariates: the number of children has highly significant effect on choice. BMI and Money are also significant. 

8. Covariates: Age and Gender have significant effects on defaultchoice. 

9. Type has significant main effect on baltho while default and the interaction between type and baltho are insignificant. 

10. For the “Forced” dataset, there is no significant effect of default on baltho. 

## •	regress the default column -> choice column (and make a bar graph of this). 

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
library("texreg")
data = readRDS(file="M:/A Master of Science in Marketing Sciences/CDC Research Assistant/HealthScreening2_1.rds")
attach(data)
defaultchoice = as.numeric(defaultchoice)
model1 = lm(choice~default)
texreg::htmlreg(l = model1, center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 1", caption.above = TRUE, digits = 4)
```

**1. Compared with non-default, the proportion of choosing 1 in the Default group is significantly higher.**

```{r, echo=FALSE}
counts <- table(data$choice,data$default)
barplot(counts, main="Barplot for Default versus Choice",
        xlab="default", col=c("darkblue","red"),
        ylim=c(0,1000))
legend("topright", legend = c("choice = 0","choice = 1"), fill = c("darkblue","red"))
```

##•	regress socialendorsement and company endorsement -> choice (look at them both in individual models and in the same model)

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
socialendorsement = as.numeric(socialendorsement)
companyendorsement = as.numeric(companyendorsement)

model2 = lm(choice~socialendorsement)
model3 = lm(choice~companyendorsement)
model4 = lm(choice~socialendorsement + companyendorsement)
texreg::htmlreg(l = list(model2, model3, model4), center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 2-4", caption.above = TRUE, digits = 4)
```

## •	regress socialendorsement and company endorsement -> defaultchoice (look at them both in individual models and in the same model)

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}

defaultchoice = as.numeric(data$defaultchoice)
model5 = lm(defaultchoice~socialendorsement)
model6 = lm(defaultchoice~companyendorsement)
model7 = lm(defaultchoice~socialendorsement + companyendorsement)
texreg::htmlreg(l = list(model5, model6, model7), center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 5-7", caption.above = TRUE, digits = 4)

```

**2. Both social endorsement and company endorsement have signficant positive effects on the probability of choosing 1.**

## •	regress endorsementcondition -> choice 
```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
model8 = lm(choice~endorsementcondition)
texreg::htmlreg(l = model8, center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 8", caption.above = TRUE, digits = 4)
```
## •	regress endorsementcondition-> defaultchoice 
```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
model9 = lm(defaultchoice~endorsementcondition)
texreg::htmlreg(l = model9, center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 9", caption.above = TRUE, digits = 4)
```
**3. EndorsementCondition does not have any significant effects on both choice and defaultchoice.**

## •	subset the data based on the type column to only the "natural" observations. Then regress smrd -> choice, baltho -> choice

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
natural = subset(data, type == "natural")
attach(natural)
smrd = as.numeric(smrd)
baltho = as.numeric(baltho)
defaultchoice = as.numeric(natural$defaultchoice)

model10 = lm(choice~smrd)
model11 = lm(choice~baltho)
texreg::htmlreg(l = list(model10, model11), center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 10-11", caption.above = TRUE, digits = 4)
```

**4. Baltho has significant effect on choice while the effect of smrd on choice is insignificant. The next regression confirms that baltho and smrd do not depend on default setting.**

## Then regress default -> smrd, default -> baltho

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
model12 = lm(smrd~natural$default)
model13 = lm(baltho~natural$default)
texreg::htmlreg(l = list(model12, model13), center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 12-13", caption.above = TRUE, digits = 4)
```
**5. baltho and smrd do not depend on default setting.**

## Then regress smrd-> defaultchoice, baltho -> defaultchoice
```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
model14 = lm(defaultchoice~smrd)
model15 = lm(defaultchoice~baltho)
texreg::htmlreg(l = list(model14, model15), center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 14-15", caption.above = TRUE, digits = 4)
```
**6. Reverse to Summary 4, Baltho has insignificant effect on choice while the effect of smrd on choice is significant.**

## •	Regress Race, Age, Gender, Ethnicity, Marital, Children, BMI, Exercise, Smoke,  Own Health, Family, Friend, Career, PersonalHealth, Money -> choice (all in one model, no interactions)

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
attach(data)
Age = as.numeric(data$Age)
Gender = as.factor(data$Gender)
Marital = as.factor(data$Marital)
Children = as.numeric(data$Children)
Ethnicity = as.factor(data$Ethnicity)
## Education = as.factor(Education)
Exercise = as.numeric(data$Exercise)
## Should "Exercise" be as.numeic or as.factor?
Smoke = as.factor(data$Smoke)
Own_Health = as.numeric(data$Own_Health)
## Should "OwnHealth" be as.numeic or as.factor?
Family = as.numeric(data$Family)
Friend = as.numeric(data$Friend)
Career = as.numeric(data$Career)
PersonalHealth = as.numeric(data$PersonalHealth)
Money = as.numeric(data$Money)

model16 = lm(choice~Race + Age + Gender + Marital + Children + Ethnicity + BMI + Exercise + Smoke + Own_Health + Family + Friend + Career + PersonalHealth + Money)
texreg::htmlreg(l = model16, center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 16", caption.above = TRUE, digits = 4)

```
**7. Covariates: the number of children has highly significant effect on choice. BMI and Money are also significant.**

## •	Regress Race, Age, Gender, Ethnicity, Marital, Children, BMI, Exercise, Smoke,  Own Health, Family, Friend, Career, PersonalHealth, Money -> defaultchoice (all in one model, no interactions)

```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
model17 = lm(data$defaultchoice~ Race + Age + Gender + Marital + Children + Ethnicity + BMI + Exercise + Smoke + Own_Health + Family + Friend + Career + PersonalHealth + Money)
texreg::htmlreg(l = model17, center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 17", caption.above = TRUE, digits = 4)
```
**8. Covariates: Age and Gender have significant effects on defaultchoice.**

## •	Regress type*default -> baltho 
```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
attach(data)
data$baltho = as.numeric(data$baltho)
type = as.factor(type)
default = as.factor(default)
model18 = lm(data$baltho~type + default + type * default)
texreg::htmlreg(l = model18, center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 18", caption.above = TRUE, digits = 4)
```
**9. Type has significant main effect on baltho while default and the interaction between type and baltho are insignificant.**

## •	Subset data based on type column to only "forced" observations and do an anova comparing the baltho for the the default column. (so anova for default -> baltho). 
```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
force = subset(data, type == "forced")
attach(force)
fit <- aov(baltho ~ default, data = force)
```

```{r chunkTest, echo=FALSE, results='asis', warning = FALSE}
library(xtable)
# Coefficients
# print(fit, type = "html")
# Analysis of variance.
print(xtable(fit), type = "html")
```
**10. For the “Forced” dataset, there is no significant effect of default on baltho.**

## •	bar graphs of all the demographics variables ##
```{r,echo=FALSE,results='hide',message=FALSE}
attach(data)
```
```{r, echo=FALSE, warning=FALSE}
counts <- table(Race)
barplot(counts, main="Race Distribution", xlab="Race")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Age)
barplot(counts, main="Age Distribution", xlab="Age")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Gender)
barplot(counts, main="Gender Distribution", xlab="Gender")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Ethnicity)
barplot(counts, main="Ethnicity Distribution", xlab="Ethnicity")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Marital)
barplot(counts, main="Marital Status Distribution", xlab="Marital Status")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Children)
barplot(counts, main="Children Distribution", xlab="Number of Children")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(BMI)
barplot(counts, main="BMI Distribution", xlab="BMI")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Exercise)
barplot(counts, main="Exercise Distribution", xlab="Exercise")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Smoke)
barplot(counts, main="Smoke Distribution", xlab="Smoke")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Own_Health)
barplot(counts, main="Own Health Distribution", xlab="Own health")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Family)
barplot(counts, main="Family Distribution", xlab="Family")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Friend)
barplot(counts, main="Friend Distribution", xlab="Friend")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Career)
barplot(counts, main="Career Distribution", xlab="Career")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(PersonalHealth)
barplot(counts, main="Personal Health Distribution", xlab="Personal Health")
```

```{r, echo=FALSE, warning=FALSE}
counts <- table(Money)
barplot(counts, main="Money Distribution", xlab="Money")
```

## •	regress endorsement condition on social and company endorsement. 
```{r, echo=FALSE, warning=FALSE, results = 'asis',message=FALSE}
attach(data)
model20 = lm(socialendorsement~endorsementcondition)
model21 = lm(companyendorsement~endorsementcondition)
texreg::htmlreg(l = list(model20,model21), center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 20-21", caption.above = TRUE, digits = 4)
```

### 
```{r, echo=FALSE, warning=FALSE, results = 'asis',message=FALSE}
attach(natural)
model22 = lm(smrd~as.factor(endorsementcondition),data = natural)
model23 = lm(smrd~as.numeric(socialendorsement),data = natural)
model24 = lm(smrd~as.numeric(companyendorsement),data = natural)
model25 = lm(smrd~as.factor(endorsementcondition)+as.numeric(socialendorsement)+as.numeric(companyendorsement),data = natural)
texreg::htmlreg(l = list(model22,model23,model24,model25), center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 22-25", caption.above = TRUE, digits = 4)
```

### 
```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis',message=FALSE}
attach(natural)
model26 = lm(baltho~as.factor(endorsementcondition),data = natural)
model27 = lm(baltho~as.numeric(socialendorsement),data = natural)
model28 = lm(baltho~as.numeric(companyendorsement),data = natural)
model29 = lm(baltho~as.factor(endorsementcondition)+as.numeric(socialendorsement)+as.numeric(companyendorsement),data = natural)
texreg::htmlreg(l = list(model26,model27,model28,model29), center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 26-29", caption.above = TRUE, digits = 4)
```

## •	for the "forced" subset regressions of the endorsement variables on baltho
```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis',message=FALSE}
attach(force)
model30 = lm(baltho~as.factor(endorsementcondition),data = force)
model31 = lm(baltho~as.numeric(socialendorsement),data = force)
model32 = lm(baltho~as.numeric(companyendorsement),data = force)
model33 = lm(baltho~as.factor(endorsementcondition)+as.numeric(socialendorsement)+as.numeric(companyendorsement),data = force)
texreg::htmlreg(l = list(model30,model31,model32,model33), center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),bold = 0.1, caption = "Model 30-33", caption.above = TRUE, digits = 4)
```



