---
title: "SecondMediationAnalysis"
author: "Jin Miao"
date: "February 23, 2018"
output: 
  html_document:
    code_folding: hide
    highlight: haddock
    theme: paper
    toc: true
    toc_depth: 3
    toc_float: true
  pdf_document:
    toc: yes
    toc_depth: 3
subtitle: Mediation & Climate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r,message=FALSE,warning=FALSE}
data = readRDS(file="M:/A Master of Science in Marketing Sciences/CDC Research Assistant/HealthManagement2.rds")
attach(data)
data$defaultchoice = as.numeric(data$defaultchoice)
data$socialendorsement = as.numeric(data$socialendorsement)
data$companyendorsement = as.numeric(data$companyendorsement)
data$doctorendorsement = as.numeric(data$doctorendorsement)
data$Age = as.numeric(data$Age)
data$Gender = as.factor(data$Gender)
data$Marital = as.factor(data$Marital)
data$Children = as.numeric(data$Children)
data$Ethnicity = as.factor(data$Ethnicity)
data$Exercise = as.numeric(data$Exercise)
data$Smoke = as.factor(data$Smoke)
data$Own_Health = as.numeric(data$Own_Health)
data$Family = as.numeric(data$Family)
data$Friend = as.numeric(data$Friend)
data$Career = as.numeric(data$Career)
data$PersonalHealth = as.numeric(data$PersonalHealth)
data$Money = as.numeric(data$Money)
data$baltho = as.numeric(data$baltho)
data$type = as.factor(data$type)
data$default = as.factor(data$default)
data$smrd = as.numeric(data$smrd)
```

#For the natural subset 
##1. smrd mediating company endorsement on choice 
```{r,warning=FALSE,message=FALSE}
library(mediation)
natural = subset(data, type == "natural")
attach(natural)
med.fit <- lm(smrd ~ companyendorsement, data = natural)
out.fit <- glm(choice ~ smrd+ companyendorsement,data = natural, family = binomial("probit"))

med.out_1 <- mediate(med.fit, out.fit, boot = TRUE, treat = "companyendorsement", mediator = "smrd", sims = 1000)

summary(med.out_1)
plot(med.out_1,main = "The Mediation Effect of smrd on companyendorsement")
```


##2. baltho mediating company endorsement on choice
```{r,message=FALSE}
med.fit <- lm(baltho ~ companyendorsement, data = natural)
out.fit <- glm(choice ~ baltho+ companyendorsement,data = natural, family = binomial("probit"))

med.out_2 <- mediate(med.fit, out.fit, boot = TRUE, treat = "companyendorsement", mediator = "baltho", sims = 1000)

summary(med.out_2)
plot(med.out_2,main = "The Mediation Effect of baltho on companyendorsement")
```

##3. smrd mediating social endorsement on choice 
```{r,message=FALSE}
med.fit <- lm(smrd ~ socialendorsement, data = natural)
out.fit <- glm(choice ~ smrd+ socialendorsement,data = natural, family = binomial("probit"))

med.out_3 <- mediate(med.fit, out.fit, boot = TRUE, treat = "socialendorsement", mediator = "smrd", sims = 1000)

summary(med.out_3)
plot(med.out_3,main = "The Mediation Effect of smrd on socialendorsement")
```

##4. baltho mediating social endorsement on choice 
```{r,message=FALSE}
med.fit <- lm(baltho ~ socialendorsement, data = natural)
out.fit <- glm(choice ~ baltho+ socialendorsement,data = natural, family = binomial("probit"))

med.out_4 <- mediate(med.fit, out.fit, boot = TRUE, treat = "socialendorsement", mediator = "baltho", sims = 1000)

summary(med.out_4)
plot(med.out_4,main = "The Mediation Effect of baltho on socialendorsement")
```

##5. smrd mediating doctor endorsement on choice 
```{r,message=FALSE}
med.fit <- lm(smrd ~ doctorendorsement, data = natural)
out.fit <- glm(choice ~ smrd+ doctorendorsement,data = natural, family = binomial("probit"))

med.out_5 <- mediate(med.fit, out.fit, boot = TRUE, treat = "doctorendorsement", mediator = "smrd", sims = 1000)

summary(med.out_5)
plot(med.out_5,main = "The Mediation Effect of smrd on doctorendorsement")
```

##6. baltho mediating doctor endorsement on choice 
```{r,message=FALSE}
med.fit <- lm(baltho ~ doctorendorsement, data = natural)
out.fit <- glm(choice ~ baltho+ doctorendorsement,data = natural, family = binomial("probit"))

med.out_6 <- mediate(med.fit, out.fit, boot = TRUE, treat = "doctorendorsement", mediator = "baltho", sims = 1000)

summary(med.out_4)
plot(med.out_4,main = "The Mediation Effect of baltho on doctorendorsement")
```

#For the total dataset
##1. baltho mediating company endorsement on choice 
```{r,message=FALSE}
attach(data)
med.fit <- lm(baltho ~ companyendorsement, data = data)
out.fit <- glm(choice ~ baltho+ companyendorsement,data = data, family = binomial("probit"))

med.out_7 <- mediate(med.fit, out.fit, boot = TRUE, treat = "companyendorsement", mediator = "baltho", sims = 1000)

summary(med.out_6)
plot(med.out_6,main = "The Mediation Effect of baltho on companyendorsement")
```

##2. baltho mediating social endorsement on choice 
```{r,message=FALSE}
attach(data)
med.fit <- lm(baltho ~ socialendorsement, data = data)
out.fit <- glm(choice ~ baltho+ socialendorsement,data = data, family = binomial("probit"))

med.out_8 <- mediate(med.fit, out.fit, boot = TRUE, treat = "socialendorsement", mediator = "baltho", sims = 1000)

summary(med.out_5)
plot(med.out_5,main = "The Mediation Effect of baltho on socialendorsement")
```

##3. baltho mediating doctor endorsement on choice 
```{r,message=FALSE}
attach(data)
med.fit <- lm(baltho ~ doctorendorsement, data = data)
out.fit <- glm(choice ~ baltho+ doctorendorsement,data = data, family = binomial("probit"))

med.out_9 <- mediate(med.fit, out.fit, boot = TRUE, treat = "doctorendorsement", mediator = "baltho", sims = 1000)

summary(med.out_9)
plot(med.out_9,main = "The Mediation Effect of baltho on doctorendorsement")
```
